Online Verification of Commutativity

### 2020-10-15 acmPaper/paper.tex
Slightly larger Figure 4
Trim Figure 4 for better wrap

\begin{figure*}
    % TODO format nicely.
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}.}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}
    ~
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}.}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}
    ~
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline.}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

    ~
% \end{figure}
% \begin{figure}\ContinuedFloat

    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline.}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}
    ~
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline.}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Running time for various algorithms as input graph size and density scale.}
    \label{fig:timeVsSize}
\end{figure*}

>>>>

\begin{figure*}
    % TODO format nicely.
    \begin{subfigure}{0.35\linewidth}
      \includegraphics[width=\linewidth,trim=0 0 5 30,clip]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}.}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}
    %
    \hspace{-20pt}
    %
    \begin{subfigure}{0.35\linewidth}
      \includegraphics[width=\linewidth,trim=0 0 5 30,clip]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}.}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}
    %
    \hspace{-20pt}
    %
    \begin{subfigure}{0.35\linewidth}
      \includegraphics[width=\linewidth,trim=0 0 5 30,clip]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline.}
      \label{fig:sfigNaiveTvsS}
    \end{subfigure}

% \end{figure}
% \begin{figure}\ContinuedFloat

    \begin{subfigure}{0.35\linewidth}
      \includegraphics[width=\linewidth,trim=0 0 5 30,clip]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline.}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}
    %
    \hspace{-20pt}
    %
    \begin{subfigure}{0.35\linewidth}
      \includegraphics[width=\linewidth,trim=0 0 5 30,clip]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline.}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Running time for various algorithms as input graph size and density scale.}
    \label{fig:timeVsSize}
\end{figure*}
